\chapter{其他}

\section{Q1}

  If A is the initial amount put into an account, R is the annual percentage of
  interest written as a decimal, and the interest compounds annually,
  then which of the following would be an expression, in terms of A and R,
  for the interest accrued in three years?

  \subsection{解析}

    \textbf{本题问的是利息 (不算本金)}

    \begin{align*}
      A\left( 1 + R \right)^{3} - A
      &= A\left( 1 + 3R + 3R^{2} + R^{3} \right) - A \\
      &= A\left( 3R + 3R^{2} + R^{3} \right)
    \end{align*}

\section{Q2}

  A solid yellow stripe is to be painted in the middle of a certain highway.
  If 1 gallon of paint covers an area of p square feet of highway,
  how many gallons of paint will be needed to paint a stripe t inches wide
  on a stretch of highway m miles long?
  (1 mile = 5,280 feet and 1 foot =12 inches)

  \subsection{解析}

    \begin{align*}
      \frac{5280mt}{12p}
    \end{align*}

\section{Q3}

  A certain company has found that the number of labor hours required to
  produce x items is directly proportional to the square root of x. If 3
  labor hours are required to produce 20 items, how many labor hours are
  required to produce 40 items?

  \subsection{解析}

    \begin{align*}
      h &= c \sqrt{x} \\
      3 &= c \sqrt{20} \\
      c &= \frac{3}{\sqrt{20}} \\
      h &= \frac{3}{\sqrt{20}} \sqrt{40} \\
      &= 3 \sqrt{2}
    \end{align*}

\section{Q4}

  A merchant purchased a jacket for 60 and then determined a selling price
  that equaled the purchase price of the jacket plus a markup that was 25
  percent of the selling price. During a sale, the merchant discounted the
  selling price by 20 percent and sold the jacket. What was the merchant’s
  gross profit on this sale?

  \subsection{解析}

    \textbf{注意: plus a markup that was 25 percent of the selling price}

    \begin{align*}
      x &= \text{selling price} \\
      x &= 60 + 0.25 x \\
      x &= 80
    \end{align*}

    \begin{align*}
      p &= 0.8x - 60 \\
      &= 4
    \end{align*}

\section{Q5}

  A college student expects to earn at least 1,000 in interest on an initial
  investment of 20,000. If the money is invested for one year at interest
  compounded quarterly, what is the least annual interest rate that would
  achieve the goal? Give your answer to the nearest whole percent.

  \subsection{解析}

    \begin{align*}
      20000 \left( 1 + \frac{x}{4} \right)^{4} = 21000 \\
      x &= 0.05
    \end{align*}

    \textbf{答案 5\%}
